\section*{References}
\begin{frame}{\hspace{3cm}}
\centering

\vspace{1.5cm}

\begin{beamercolorbox}[sep=20pt,center,rounded=true,shadow=true]{title}
    {\fontsize{20}{24}\selectfont \textbf{References}}
\end{beamercolorbox}

\vspace{0.8cm}


\vfill

\end{frame}
%------------------------------------------------
\begin{frame}[allowframebreaks]{References}
\footnotesize
\begin{thebibliography}{99}

\bibitem{Beran1977}
Beran, R. (1977).
\newblock Minimum Hellinger Distance Estimates for Parametric Models.
\newblock \emph{The Annals of Statistics}, 5, 445--463.

\bibitem{Billingsley1968}
Billingsley, P. (1968).
\newblock \emph{Convergence of Probability Measures}.
\newblock New York: John Wiley.

\bibitem{Bingham1964}
Bingham, C. (1964).
\newblock Distributions on the Sphere and on the Projective Plane.
\newblock Doctoral dissertation, Yale University, Department of Statistics.

\bibitem{Carroll1982}
Carroll, R. J. (1982).
\newblock Adapting for Heteroscedasticity in Linear Models.
\newblock \emph{The Annals of Statistics}, 10, 1224--1233.

\bibitem{Devroye1983}
Devroye, L. (1983).
\newblock The Equivalence of Weak, Strong and Complete Convergence in $L^1$ for Kernel Density Estimates.
\newblock \emph{The Annals of Statistics}, 11, 896--904.

\bibitem{DevroyeWagner1980}
Devroye, L., and Wagner, T. J. (1980).
\newblock The Strong Uniform Consistency of Kernel Density Estimates.
\newblock In \emph{Multivariate Analysis (Vol. 5)}, ed. P. R. Krishnaiah, New York: North-Holland, pp. 59--77.

\bibitem{Gnedenko1969}
Gnedenko, B. V., Belyayev, Yu. K., and Solovyev, A. D. (1969).
\newblock \emph{Mathematical Methods of Reliability Theory}.
\newblock Translated by R. E. Barlow, New York: Academic Press.

\bibitem{Hall1985}
Hall, P. (1985).
\newblock Asymptotic Theory of Minimum Integrated Error for Multivariate Density Estimation.
\newblock In \emph{Multivariate Analysis (Vol. 6)}, ed. P. R. Krishnaiah, New York: North-Holland, pp. 289--310.

\bibitem{JohnsonKotz1970}
Johnson, N. L., and Kotz, S. (1970).
\newblock \emph{Continuous Univariate Distributions, Vol. 2}.
\newblock Boston: Houghton-Mifflin.

\bibitem{MackRosenblatt1979}
Mack, Y. P., and Rosenblatt, M. (1979).
\newblock Multivariate $k$-Nearest Neighbor Density Estimates.
\newblock \emph{Journal of Multivariate Analysis}, 9, 1--15.

\bibitem{Mardia1972}
Mardia, K. V. (1972).
\newblock \emph{Statistics of Directional Data}.
\newblock New York: Academic Press.

\bibitem{Marron1985}
Marron, J. S. (1985).
\newblock An Asymptotically Efficient Solution to the Bandwidth Problem of Kernel Density Estimation.
\newblock \emph{The Annals of Statistics}, 13, 1011--1023.

\bibitem{Parzen1962}
Parzen, E. (1962).
\newblock On Estimation of a Probability Density Function and Mode.
\newblock \emph{The Annals of Mathematical Statistics}, 33, 1065--1076.

\bibitem{Rice1984}
Rice, J. (1984).
\newblock Bandwidth Choice for Nonparametric Regression.
\newblock \emph{The Annals of Statistics}, 12, 1215--1230.

\bibitem{Rosenblatt1956}
Rosenblatt, M. (1956).
\newblock Remarks on Some Nonparametric Estimates of a Density Function.
\newblock \emph{The Annals of Mathematical Statistics}, 27, 832--837.

\bibitem{Rosenblatt1975}
Rosenblatt, M. (1975).
\newblock A Quadratic Measure of Deviation of Two-Dimensional Density Estimates and a Test of Independence.
\newblock \emph{The Annals of Statistics}, 3, 1--14.

\bibitem{SacksYlvisaker1978}
Sacks, J., and Ylvisaker, D. (1978).
\newblock Linear Estimation for Approximately Linear Models.
\newblock \emph{The Annals of Statistics}, 6, 122--137.

\bibitem{Silverman1982}
Silverman, B. W. (1982).
\newblock On the Estimation of a Probability Density Function by the Maximum Penalized Likelihood Method.
\newblock \emph{The Annals of Statistics}, 10, 795--810.

\bibitem{Spiegelman1976}
Spiegelman, C. H. (1976).
\newblock Two Techniques for Estimating Treatment Effects in the Presence of Hidden Variables: Adaptive Regression and a Solution of Reiersol's Problem.
\newblock Doctoral dissertation, Northwestern University, Department of Mathematics.

\bibitem{Stone1984}
Stone, C. J. (1984).
\newblock An Asymptotically Optimal Window Selection Rule for Kernel Density Estimates.
\newblock \emph{The Annals of Statistics}, 12, 1285--1297.

\bibitem{Wahba1975}
Wahba, G. (1975).
\newblock Optimal Convergence Properties of Variable Knot, Kernel and Orthogonal Series Methods for Density Estimation.
\newblock \emph{The Annals of Statistics}, 3, 15--29.

\bibitem{WegmanWright1983}
Wegman, E. J., and Wright, T. W. (1983).
\newblock Splines in Statistics.
\newblock \emph{Journal of the American Statistical Association}, 78, 351--366.

\end{thebibliography}
\end{frame}

---------------------
